### 2010-03-03 doc/tech_doc/a-rex/arex_tech_doc.tex
add support for multiple session directories

\begin{itemize}
\item \textbf{\textit{mail}}\textit{=e-mail\_address} -- specifies an email
address \textbf{from} which notification mails are sent.
\item \textbf{\textit{defaultttl}}\textit{=ttl {[}ttr]} -- specifies the
time in seconds for the SD to be available after job finishes (\emph{ttl})
and after job was deleted (\emph{ttr}) due to \emph{ttl}. Defaults
are 7 days for \emph{ttl} and 30 days for \emph{ttr}. The minumum value
for both parameters is 2 hours.
\item \textbf{\textit{lrms}}\textit{=default\_lrms\_name default\_queue\_name}
-- specifies names for the LRMS and queue. Queue name can also be specified
in the JD (currently it is not allowed to override LRMS by using
the JD).
\item \textbf{\textit{sessiondir}}\textit{=path} -- specifies path to
  the directory in which the SD is created. If \emph{path} is {*} the
  default sessiondir is used -- \textit{\$HOME/.jobs}.
\item \textbf{\textit{cachedir}}\textit{=path {[}link\_path]} --
  specifies a directory to store cached data (see section
  \ref{sec:cache}). Multiple cache directories may be specified by
  specifying multiple \emph{cachedir} commands. Cached data will be
  distributed over multiple caches according to free space in
  each. Specifying no \emph{cachedir} command or commands with an
  empty path disables caching. The optional \textit{link\_path} specifies
  the path at which \emph{path} is accessible on computing nodes, if
  it is different from the path on the A-REX host. If
  \textit{link\_path} is set to '.'  files are not soft-linked, nor
  are per-job links created, but files are copied to the session
  directory. If a cache directory needs to be drained, then
  \emph{cachedir} should specify \emph{``drain''} as the
  \emph{link\_path}.
\item \textbf{\textit{remotecachedir}}\textit{=path {[}link\_path]} -
  specifies caches which are under the control of other A-REXs, but which
  this A-REX can have read-only access to (see
  Section~\ref{sec:remotecaches}).  Multiple remote cache directories may be
  specified by specifying multiple \emph{remotecachedir} commands. If
  a file is not available in paths specified by cachedir, the A-REX looks
  in remote caches. \emph{link\_path} has the same meaning as in
  \emph{cachedir}, but the special path ``replicate'' means files will
  be replicated from remote caches to local caches when they are requested.
\item \textbf{\textit{cachesize}}\textit{=high\_mark {[}low\_mark]} --
  specifies high and low watermarks for space used on the file system
  on which the cache directory is located, as a percentage of total
  file system capacity. When the max is exceeded, files will be
  deleted to bring the used space down to the min level. It is a good
  idea to have each cache on its own separate file system. To turn off
  this feature, \char`\"{}cachesize\char`\"{} without parameters can
  be specified. These cache settings apply to all caches specified by
  \emph{cachedir} commands.
\item \textbf{\textit{cacheloglevel}}\textit{=number} -- specified the
  level of logging by the \emph{cache-clean} tool, between 0 (FATAL)
  and 5 (DEBUG). Defaults to 3 (INFO).
\item \textbf{\textit{maxrerun}}\textit{=number} -- specifies maximal number
of times job will be allowed to rerun after it failed at any stage.
Default value is \emph{5}. This only specifies a upper limit. The actual
number is provided in job description and defaults to 0.
\item \textbf{\textit{maxtransfertries}}\textit{=number} -- specifies
  the maximum number of times download and upload will be attempted
  per job (retries are only performed if an error is judged to be
  temporary). This number must be greater than 0 and defaults to 10.
\end{itemize}

>>>>

\item \textbf{\textit{mail}}\textit{=e-mail\_address} -- specifies an email
address \textbf{from} which notification mails are sent.
\item \textbf{\textit{defaultttl}}\textit{=ttl {[}ttr]} -- specifies the
time in seconds for the SD to be available after job finishes (\emph{ttl})
and after job was deleted (\emph{ttr}) due to \emph{ttl}. Defaults
are 7 days for \emph{ttl} and 30 days for \emph{ttr}. The minumum value
for both parameters is 2 hours.
\item \textbf{\textit{lrms}}\textit{=default\_lrms\_name default\_queue\_name}
-- specifies names for the LRMS and queue. Queue name can also be specified
in the JD (currently it is not allowed to override LRMS by using
the JD).
\item \textbf{\textit{sessiondir}}\textit{=path [drain]} - specifies
  the path to the directory in which the SD is created. Multiple
  session directories may be specified by specifying multiple
  \emph{sessiondir} commands. In this case jobs are spread evenly over
  the session directories. If the path is {*} the default sessiondir
  is used - \textit{\$HOME/.jobs}. When adding a new session
  directory, ensure to restart the A-REX so that jobs assigned there
  are processed. A session directory can be drained prior to removal
  by adding the \emph{``drain''} option (no restart is required in
  this case). No new jobs will be assigned to this session directory
  but running jobs will still be accessible. When all jobs are
  processed and the session directory is empty, it can be removed and
  the A-REX should be restarted.
\item \textbf{\textit{cachedir}}\textit{=path {[}link\_path]} --
  specifies a directory to store cached data (see section
  \ref{sec:cache}). Multiple cache directories may be specified by
  specifying multiple \emph{cachedir} commands. Cached data will be
  distributed over multiple caches according to free space in
  each. Specifying no \emph{cachedir} command or commands with an
  empty path disables caching. The optional \textit{link\_path} specifies
  the path at which \emph{path} is accessible on computing nodes, if
  it is different from the path on the A-REX host. If
  \textit{link\_path} is set to '.'  files are not soft-linked, nor
  are per-job links created, but files are copied to the session
  directory. If a cache directory needs to be drained, then
  \emph{cachedir} should specify \emph{``drain''} as the
  \emph{link\_path}.
\item \textbf{\textit{remotecachedir}}\textit{=path {[}link\_path]} -
  specifies caches which are under the control of other A-REXs, but which
  this A-REX can have read-only access to (see
  Section~\ref{sec:remotecaches}).  Multiple remote cache directories may be
  specified by specifying multiple \emph{remotecachedir} commands. If
  a file is not available in paths specified by cachedir, the A-REX looks
  in remote caches. \emph{link\_path} has the same meaning as in
  \emph{cachedir}, but the special path ``replicate'' means files will
  be replicated from remote caches to local caches when they are requested.
\item \textbf{\textit{cachesize}}\textit{=high\_mark {[}low\_mark]} --
  specifies high and low watermarks for space used on the file system
  on which the cache directory is located, as a percentage of total
  file system capacity. When the max is exceeded, files will be
  deleted to bring the used space down to the min level. It is a good
  idea to have each cache on its own separate file system. To turn off
  this feature, \char`\"{}cachesize\char`\"{} without parameters can
  be specified. These cache settings apply to all caches specified by
  \emph{cachedir} commands.
\item \textbf{\textit{cacheloglevel}}\textit{=number} -- specified the
  level of logging by the \emph{cache-clean} tool, between 0 (FATAL)
  and 5 (DEBUG). Defaults to 3 (INFO).
\item \textbf{\textit{maxrerun}}\textit{=number} -- specifies maximal number
of times job will be allowed to rerun after it failed at any stage.
Default value is \emph{5}. This only specifies a upper limit. The actual
number is provided in job description and defaults to 0.
\item \textbf{\textit{maxtransfertries}}\textit{=number} -- specifies
  the maximum number of times download and upload will be attempted
  per job (retries are only performed if an error is judged to be
  temporary). This number must be greater than 0 and defaults to 10.
